\huge \systemEnding: Growing Libraries of Concepts with Wake-Sleep Program Induction

### 2018-07-22 misc2.tex
improvements to talk and poster
Improving the LOGO part

Agent controls a `pen' tasked with drawing pictures.

  \includegraphics[width=20cm]{figures/poster2/sampleTasks.png}

>>>>

  \includegraphics[width=\twocolwid]{figures/dreams/montageLearningAndShapes.eps}

  \textbf{Left column:} 16 out of 92 example tasks to hit in an all-or-none
  fashion --- training set for the \system algorithm.
  \textbf{Right column:} Learning curve for a run with a timeout of search time
  per task of 5 minutes (blue, bottom) and of 120 minutes (red, top). On the
  bottom are dreams, from left to right: before any training (original DSL, flat
  priors), at the end of the 5-minutes-timeout run, and at the end of the
  12-minutes-timeout run.

\end{column}
\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
  The agent controls a `pen' on a 2D plant. Primitives are those of the LOGO
  language, modified to have a functional programing structure.
\end{column}
\end{columns}
